BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-01-26 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
typo

The data exporting module contains three functions, which interact with LaTeX templates and require slightly more advanced R user interactivity such as setting up mapping functions using the tidyverses purrr package.
*labels_skeleton* is an R script which will require a few modification steps to tailor to each instiution, these r scripts will put data into a TEMPLATE...

>>>>

The data exporting module contains three functions, which interact with LaTeX templates and require slightly more advanced R user interactivity such as setting up mapping functions using the tidyverses purrr package.
*labels_skeleton* is an R script which will require a few modification steps to tailor to each institution, these r scripts will put data into a TEMPLATE...
